A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-11-08 manuscript.Rmd
fixes in bibliography added keywords

keywords          : "keywords"
wordcount         : "`r tryCatch(wordcountaddin::word_count(here::here('manuscript.Rmd')), error=function(err) 'NA')`"

>>>>

keywords          : "reproducibility, R, version management, literate programming, dependency management, containerization, open science"
wordcount         : "`r tryCatch(wordcountaddin::word_count(here::here('manuscript.Rmd')), error=function(err) 'NA')`"
